Simulation pipeline

### 2024-04-22 Analysis/02_Simulation_pipeline.Rmd
Update 02_Simulation_pipeline.Rmd

## Checking the results

@@

```{r, eval = FALSE}
source("../Functions/analyse.replicates.R")
## Check the change in variance for all 120 parameters
analyse.replicates("../Data/Processed/sim_filtering.rda") #140 -> #170
analyse.replicates("../Data/Processed/sim_equalizing.rda") #155
analyse.replicates("../Data/Processed/sim_competition.rda") #126
analyse.replicates("../Data/Processed/sim_facilitation.rda") #163
```

>>>>

<!-- 
## Checking the results

@@

```{r, eval = FALSE}
source("../Functions/analyse.replicates.R")
## Check the change in variance for all 120 parameters
analyse.replicates("../Data/Processed/sim_filtering.rda") #140 -> #170
analyse.replicates("../Data/Processed/sim_equalizing.rda") #155
analyse.replicates("../Data/Processed/sim_competition.rda") #126
analyse.replicates("../Data/Processed/sim_facilitation.rda") #163
``` -->
